How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-04-22 Paper/paper.tex

Several studies have shown that block-based languages are powerful as a tool for teaching programming~\cite{meerbaum-salant_learning_2010, b._moskal_evaluating_2005,cooper_teaching_2003}. Research works involving static analysis of Scratch programs \cite{Maloney_2008} \cite{moreno_automatic_2014} have evaluated the use of various programming concepts in 536 and 100 Scratch projects respectively. Recent work has focused on bad programming practices and habits within Scratch programs \cite{Meerbaum_habits_2011}, and automated quality assessment tools have been proposed for identifying code smells and bad programming practices \cite{boe_hairball:_2013}\cite{moreno_automatic_2014}. Ar recent controlled experiment found that long scripts and duplication decreases a novice programmer's ability to understand and modify Scratch programs \cite{hermans_2016}.

@@

Also related to our research are works on code smells, initiated by the work by Fowler~\cite{fowler_refactoring:_1999}. His book gives an overview of code smells and corresponding refactorings. Fowler's work was followed by efforts focused on the automatic identification of code smells by means of metrics. Marinescu~\cite{marinescu_detecting_2001} for instance, uses metrics to identify \emph{suspect} classes: classes which could have design flaws. Alves \emph{et al.}~\cite{alves_deriving_2010} focus on a strategy to obtain thresholds for metrics from a benchmark Moha \emph{et al.}~\cite{moha_decor:_2010} designed the `DECOR' method which automatically generates a smell detection algorithms from specifications. The CCFinder tool~\cite{kamiya_ccfinder:_2002} finally, aims at detecting clones in source code, which are similar to our code duplication smell.

>>>>

Several studies have shown that block-based languages are powerful as a tool for teaching programming~\cite{meerbaum-salant_learning_2010, b._moskal_evaluating_2005,cooper_teaching_2003}. Research works involving static analysis of Scratch programs \cite{Maloney_2008} \cite{moreno_automatic_2014} have evaluated the use of various programming concepts in 536 and 100 Scratch projects respectively. Recent work has focused on bad programming practices and habits within Scratch programs \cite{Meerbaum_habits_2011}, and automated quality assessment tools have been proposed for identifying code smells~\cite{fowler_refactoring:_1999}~and bad programming practices \cite{boe_hairball:_2013}\cite{moreno_automatic_2014}. Ar recent controlled experiment found that long scripts and duplication decreases a novice programmer's ability to understand and modify Scratch programs \cite{hermans_2016}.

@@

%Also related to our research are works on code smells, initiated by the work by Fowler~\cite{fowler_refactoring:_1999}. His book gives an overview of code smells and corresponding refactorings. Fowler's work was followed by efforts focused on the automatic identification of code smells by means of metrics. Marinescu~\cite{marinescu_detecting_2001} for instance, uses metrics to identify \emph{suspect} classes: classes which could have design flaws. Alves \emph{et al.}~\cite{alves_deriving_2010} focus on a strategy to obtain thresholds for metrics from a benchmark Moha \emph{et al.}~\cite{moha_decor:_2010} designed the `DECOR' method which automatically generates a smell detection algorithms from specifications. The CCFinder tool~\cite{kamiya_ccfinder:_2002} finally, aims at detecting clones in source code, which are similar to our code duplication smell.
